Evolution of solar wind discontinuities in the inner heliosphere

### 2025-10-06 index.qmd
feat: add citations and expand dataset descriptions for PSP, Wind and ARTEMIS missions

@@

In this study, we utilize magnetic field and plasma measurements from multiple spacecraft. For the Parker Solar Probe (PSP), we use magnetic field data from the FIELDS instrument and plasma data from the Solar Probe ANalyzer (SPAN) suite. The proton and electron anisotropies are derived from the corresponding SPAN-Ion and SPAN-Electron measurements. For the Wind and ARTEMIS missions, magnetic field data are obtained from the onboard magnetometers, while plasma parameters are taken from the Faraday cup instrument on Wind and the corresponding plasma instrument on ARTEMIS.

@@

For this study

@@

>>>>

@huangTemperatureAnisotropyHelium2025 : alfvénic slow solar wind 
@larosaSwitchbacksStatisticalProperties2021 : Switchbacks: statistical properties and deviations from Alfvénicity

@@

We utilize magnetic field and plasma measurements from the Parker Solar Probe (PSP) mission [@foxSolarProbeMission2016], ARTEMIS mission [@angelopoulosARTEMISMission2011], and Wind mission [@acunaGlobalGeospaceScience1995]. For PSP, we utilized high-resolution magnetic field from the FIELDS instrument [@baleFIELDSInstrumentSuite2016] and proton, electron and alpha measurements from the FIELDS and SWEAP instruments [@kasperSolarWindElectrons2016]. More specifically, the proton and electron temperature anisotropies are derived from the corresponding SPAN-Ion and SPAN-Electron measurements [@whittleseySolarProbeANalyzers2020; @liviSolarProbeANalyzer2022]. For the Wind and ARTEMIS missions, magnetic field data are obtained from the onboard magnetometers, while plasma parameters are taken from the Faraday cup instrument on Wind and the corresponding plasma instrument on ARTEMIS.

@@

@@

<!-- For the Wind data used in this work, the Solar Wind  Experiment Faraday cup measures the reduced VDFs of solar wind protons and helium along 40 angles every 92 s (K. Ogilvie  et al. 1995), and the Magnetic Field Investigation provides the  magnetic field data (R. Lepping et al. 1995; A. Koval & A. Szabo 2013). The proton temperature anisotropies are derived by fitting  the spectra with a convected bi-Maxwellian function (J. C. Kasper  et al. 2007).
 -->
